Space-time plots

### 2016-04-07 Rmd/space-time.Rmd
Intro paragraphs of paper drafted. Slight tweaks to select-titles.Rmd.

# labels for temporal axes
# return interval
tlab1 <- c(expression("second"^-1), expression("minute"^-1),
           expression("hour"^-1), expression("day"^-1), 
           expression("week"^-1), expression("month"^-1),            
           expression("year"^-1), expression("decade"^-1),
           expression("century"^-1), 
           expression("millenium"^-1), "once-off")# expression(infinity))
taxis1 <- cbind.data.frame( 
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis1 <- data.table(taxis1)
setnames(taxis1, names(taxis1), "days")
taxis1[, logdays := log10(days)]

taxis2 <- cbind.data.frame(
  c("second", "minute", "hour", "day", "week", "month", "year", "decade",
    "century", "millenium", "10 KA"),  
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis2 <- data.table(taxis2)
setnames(taxis2, names(taxis2), c("label", "days"))
taxis2[, logdays := log10(days)]

@@

# plot resolution
alab1 <- c(expression("0.01 cm"^2), expression("0.1 cm"^2), 
           expression("1 cm"^2), expression("10 cm"^2),
           expression("100 cm"^2), expression("1000 cm"^2), 
           expression("1 m"^2), expression("10 m"^2),
           expression("100 m"^2), expression("1000 m"^2), 
           "1 ha", "10 ha", "100 ha", "1000 ha", "10000 ha")

@@

# sampled area
alab2 <- c(expression("1 m"^2), expression("10 m"^2), expression("100 m"^2),
           expression("1000 m"^2), expression("1 ha"), expression("10 ha"),
           expression("100 ha"), expression("1000 ha"), 
           expression(paste(10^4 , " ha")), expression(paste(10^5 , " ha")), 
           expression(paste(10^6 , " ha")), expression(paste(10^7 , " ha")), 
           expression(paste(10^8 , " ha")), expression(paste(10^9 , " ha")), 
           expression(paste(10^10 , " ha")))

@@

cxa = 0.7
pdf("paper/figures/res_v_extent_pbstrap.pdf", width = 7, 
    height = 2.5)
par(mfrow = c(1, 2), mar = c(4, 4, 0.3, 3), oma = c(0, 0, 0, 1), 
    mgp = c(2, 0.5, 0))
# image(rres, col = cols, breaks = brks,
image(rres, col = rev(terrain.colors(30)), breaks = brks,
     axes = FALSE, xlab = "", ylab = "")
# plot(rres2, col = rev(terrain.colors(20)))
axis(1, at = taxis1$logdays[-c(5, 9, 10)], labels = tlab1[-c(5, 9, 10)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = aaxis1$logres[-1], labels = alab1[-1], las = 2, tcl = -0.2, 
     cex.axis = cxa)
# plot(rres2, axes = FALSE, legend.only = TRUE)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs, labels = brklabs, 
              cex.axis = cxa, tcl = -0.1)
plot(rres, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks, col = rev(terrain.colors(30)))
image(rext, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = taxis2$label[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
plot(rext, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()

@@

image(rext2, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = taxis2$label[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
plot(rext2, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()

@@

@@

cxa = 0.7
pdf("paper/figures/res_v_extent.pdf", width = 7, 
    height = 2.5)
par(mfrow = c(1, 2), mar = c(4, 4, 0.3, 3), oma = c(0, 0, 0, 1), 
    mgp = c(2, 0.5, 0))
image(rres3, col = rev(terrain.colors(30)), breaks = brks,
     axes = FALSE, xlab = "", ylab = "")
axis(1, at = taxis1$logdays[-c(5, 9, 10)], labels = tlab1[-c(5, 9, 10)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = aaxis1$logres[-1], labels = alab1[-1], las = 2, tcl = -0.2, 
     cex.axis = cxa)

@@

image(rext3, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = taxis2$label[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
plot(rext3, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()

>>>>

# labels for temporal axes
# return interval
tlab1 <- c(expression(paste(NULL<="second"^-1)), expression("minute"^-1),
           expression("hour"^-1), expression("day"^-1), 
           expression("week"^-1), expression("month"^-1),            
           expression("year"^-1), expression("decade"^-1),
           expression("century"^-1), 
           expression("millenium"^-1), "once-off")# expression(infinity))
taxis1 <- cbind.data.frame( 
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis1 <- data.table(taxis1)
setnames(taxis1, names(taxis1), "days")
taxis1[, logdays := log10(days)]

tlab2 <- c(expression(NULL<="second"), "minute", "hour", "day", "week", "month",
           "year","decade", "century", "millenium", "10 KA")  
taxis2 <- cbind.data.frame(c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30,
                             365, 365 * 10, 365 * 100, 365 * 1000, 365 * 10000))
taxis2 <- data.table(taxis2)
setnames(taxis2, names(taxis2), c("days"))
taxis2[, logdays := log10(days)]

@@

# plot resolution
alab1 <- c(expression(paste(NULL<="0.01 cm"^2)), expression("0.1 cm"^2), 
           expression("1 cm"^2), expression("10 cm"^2),
           expression("100 cm"^2), expression("1000 cm"^2), 
           expression("1 m"^2), expression("10 m"^2),
           expression("100 m"^2), expression("1000 m"^2), 
           "1 ha", "10 ha", "100 ha", "1000 ha", 
           expression(paste(NULL>="10000 ha")))

@@

# sampled area
alab2 <- c(expression(paste(NULL<="1 m"^2)), expression("10 m"^2), 
           expression("100 m"^2), expression("1000 m"^2), expression("1 ha"),
           expression("10 ha"), expression("100 ha"), expression("1000 ha"), 
           expression(paste(10^4 , " ha")), expression(paste(10^5 , " ha")), 
           expression(paste(10^6 , " ha")), expression(paste(10^7 , " ha")), 
           expression(paste(10^8 , " ha")), expression(paste(10^9 , " ha")), 
           expression(paste(10^10 , " ha")))

@@

cxa = 0.7
pdf("paper/figures/res_v_extent_pbstrap.pdf", width = 7, 
    height = 2.5)
par(mfrow = c(1, 2), mar = c(4, 4, 0.3, 3), oma = c(0, 0, 0, 1), 
    mgp = c(2, 0.5, 0))
# image(rres, col = cols, breaks = brks,
image(rres, col = rev(terrain.colors(30)), breaks = brks,
     axes = FALSE, xlab = "", ylab = "")
# plot(rres2, col = rev(terrain.colors(20)))
axis(1, at = taxis1$logdays[-c(5, 9, 10)], labels = tlab1[-c(5, 9, 10)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = aaxis1$logres[-1], labels = alab1[-1], las = 2, tcl = -0.2, 
     cex.axis = cxa)
# plot(rres2, axes = FALSE, legend.only = TRUE)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs, labels = brklabs, 
              cex.axis = cxa, tcl = -0.1)
plot(rres, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks, col = rev(terrain.colors(30)))
image(rext, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
plot(rext, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()

@@

image(rext2, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
plot(rext2, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()

@@

# temporal framing
tempdat <- data.table(x = log10(to_infin_byond(datf$t_btwn_samp)), 
                      y = log10(datf$study_duration))
tempdat$n <- rep(1, nrow(tempdat))
tx <- range(tempdat$x)
tx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
tx[2] <- 6.56
tempdat[x < rx[1], x := rx[1]]
tempdat[x > rx[2], x := rx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ty[1]), 5.56)#ceiling(ex[2]))
tempdat[y < ty[1], y := ty[1]]
tempdat[y > ty[2], y := ty[2]]
coordinates(tempdat) <- ~x + y

# spatial framing
spatdat <- data.table(x = log10(datf$plot_res), y = log10(datf$sampled_area))
spatdat$n <- rep(1, nrow(spatdat))
sx <- range(aaxis1$logres)
sx[1] <- -5  # set limits to 0.01 cm^2
spatdat[x < sx[1], y := sx[1]]
spatdat[x > sx[2], y := sx[2]]
sy <- range(aaxis2$logarea)
spatdat[y < sy[1], y := sy[1]]
spatdat[y > sy[2], y := sy[2]]
coordinates(spatdat) <- ~x + y

@@

# # temporal
# tres <- kdensity(tx[1], tx[2], ty[1], ty[2], 0.1, tempdat, 1)
# #spatial
# sres <- kdensity(sx[1], sx[2], sy[1], sy[2], 0.1, spatdat, 1)
# image(sres, col = rev(terrain.colors(30)))

cxa = 0.7
pdf("paper/figures/res_v_extent.pdf", width = 7, 
    height = 2.5)
par(mfrow = c(1, 2), mar = c(4, 4, 0.3, 3), oma = c(0, 0, 0, 1), 
    mgp = c(2, 0.5, 0))
image(rres3, col = rev(terrain.colors(30)), breaks = brks,
     axes = FALSE, xlab = "", ylab = "")
axis(1, at = taxis1$logdays[-c(5, 9, 10)], labels = tlab1[-c(5, 9, 10)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = aaxis1$logres[-1], labels = alab1[-1], las = 2, tcl = -0.2, 
     cex.axis = cxa)
mtext("Sampling interval", 1, cex = cxa, line = 3)
mtext("Spatial resolution", 2, cex = cxa, line = 3)

@@

image(rext3, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = tlab2[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 0.25, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa, tcl = -0.1)
mtext("Temporal duration", 1, cex = cxa, line = 3)
mtext("Spatial extent", 2, cex = cxa, line = 3)

plot(rext3, legend.only = TRUE, axis.args = aargs, legend.width = 1.25,
     legend.shrink = 0.9, breaks = brks2, col = rev(terrain.colors(30)))
dev.off()
